Fréchet Distance

### 2022-12-05 docs/paper.tex
removed name for peer review

%%% sets the PDF-Information options
%%% (see fields in Acrobat Reader: ``File -> Document properties -> Summary'')
%%% Note: this method is better than as options of the hyperref-package (options are expanded correctly)
\hypersetup{
  pdftitle={Fréchet Distance}, %%
  pdfauthor={Tom Stein}, %%
  pdfsubject={Seminar Algorithm Engineering 22/23}, %%
  pdfcreator={Accomplished with LaTeX2e and pdfLaTeX with hyperref-package.}, %% 
  pdfproducer={}, %%
  pdfkeywords={} %%
}

@@

%%% author(s)
\author{Tom Stein}

>>>>

%%% sets the PDF-Information options
%%% (see fields in Acrobat Reader: ``File -> Document properties -> Summary'')
%%% Note: this method is better than as options of the hyperref-package (options are expanded correctly)
\hypersetup{
  pdftitle={Fréchet Distance}, %%
  % pdfauthor={Tom Stein}, %%
  pdfsubject={Seminar Algorithm Engineering 22/23}, %%
  pdfcreator={Accomplished with LaTeX2e and pdfLaTeX with hyperref-package.}, %% 
  pdfproducer={}, %%
  pdfkeywords={} %%
}

@@

%%% author(s)
% \author{Tom Stein}
